Two sample $t$ test example using `nycflights13` `flights` data

### 2018-05-13 inst/doc/chisq_test.Rmd
Update vignettes

@@

```{r}
chisq_null_distn %>% 
  dplyr::summarize(p_value = mean(stat >= obs_chisq)) %>% 
  dplyr::pull()
```

@@

```{r }
fli_small %>%
  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
  hypothesize(null = "independence") %>%
  # generate() ## Not used for theoretical
  calculate(stat = "Chisq") %>%
  visualize(method = "theoretical", obs_stat = obs_chisq, direction = "right")
```

@@

```{r eval=FALSE}
fli_small %>%
  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "Chisq") %>% 
  visualize(method = "both", obs_stat = obs_chisq, direction = "right")
```

>>>>

**Note**: The `type` argument in `generate()` is automatically filled based on the entries for `specify()` and
`hypothesize()`. It can be removed throughout the examples that follow. It is left in to reiterate the type of generation process being performed.

@@

```{r}
chisq_null_distn %>% 
  dplyr::summarize(p_value = mean(stat >= pull(obs_chisq))) %>% 
  dplyr::pull()
```

@@

```{r }
fli_small %>%
  specify(origin ~ season) %>% 
  hypothesize(null = "independence") %>%
  # generate() ## Not used for theoretical
  calculate(stat = "Chisq") %>%
  visualize(method = "theoretical", obs_stat = obs_chisq, direction = "right")
```

@@

```{r eval=FALSE}
fli_small %>%
  specify(origin ~ season) %>%  %>% # alt: response = origin, explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "Chisq") %>% 
  visualize(method = "both", obs_stat = obs_chisq, direction = "right")
```

### 2018-05-13 inst/doc/flights_examples.Rmd
Update vignettes

---
title: "Randomization Examples using `nycflights13` `flights` data"
author: "Chester Ismay and Andrew bray"
date: "2018-01-05"
output: 
  rmarkdown::html_vignette:
    df_print: kable
vignette: |
  %\VignetteIndexEntry{flights example}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

```{r message=FALSE, warning=FALSE}
library(nycflights13)
library(dplyr)
library(ggplot2)
library(stringr)
library(infer)
set.seed(2017)
fli_small <- flights %>% 
  sample_n(size = 500) %>% 
  mutate(season = case_when(
    month %in% c(10:12, 1:3) ~ "winter",
    month %in% c(4:9) ~ "summer"
  )) %>% 
  mutate(day_hour = case_when(
    between(hour, 1, 12) ~ "morning",
    between(hour, 13, 24) ~ "not morning"
  )) %>% 
  select(arr_delay, dep_delay, season, 
         day_hour, origin, carrier) %>%
  filter(., complete.cases(.))
```

@@

```{r}
x_bar <- fli_small %>%
  summarize(mean(dep_delay)) %>%
  pull()
null_distn <- fli_small %>%
  specify(response = dep_delay) %>%
  hypothesize(null = "point", mu = 10) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "mean")
ggplot(data = null_distn, mapping = aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = x_bar, color = "red")
null_distn %>%
  summarize(p_value = mean(stat > x_bar) * 2)
```

@@

```{r}
x_tilde <- fli_small %>%
  summarize(median(dep_delay)) %>%
  pull()
null_distn <- fli_small %>%
  specify(response = dep_delay) %>%
  hypothesize(null = "point", med = 0) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "median")
ggplot(null_distn, aes(x = stat)) +
  geom_bar() +
  geom_vline(xintercept = x_tilde, color = "red")
null_distn %>%
  summarize(p_value = mean(stat < x_tilde) * 2)
```

@@

```{r}
p_hat <- fli_small %>%
  summarize(mean(day_hour == "morning")) %>%
  pull()
null_distn <- fli_small %>%
  specify(response = day_hour, success = "morning") %>%
  hypothesize(null = "point", p = .5) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "prop")
ggplot(null_distn, aes(x = stat)) +
  geom_bar() +
  geom_vline(xintercept = p_hat, color = "red")
null_distn %>%
  summarize(p_value = mean(stat < p_hat) * 2)
```

@@

```{r}
d_hat <- fli_small %>%
  group_by(season) %>%
  summarize(prop = mean(day_hour == "morning")) %>%
  summarize(diff(prop)) %>%
  pull()
null_distn <- fli_small %>%
  specify(day_hour ~ season, success = "morning") %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "diff in props", order = c("summer", "winter"))
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = d_hat, color = "red")
null_distn %>%
  summarize(p_value = mean(stat < d_hat) * 2)
```

@@

```{r}
Chisq_hat <- chisq.test(table(fli_small$origin))$stat
null_distn <- fli_small %>%
  specify(response = origin) %>%
  hypothesize(null = "point", 
              p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "Chisq")
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = Chisq_hat, color = "red")
null_distn %>%
  summarize(p_value = mean(stat > Chisq_hat)) 
```

@@

```{r}
Chisq_hat <- chisq.test(table(fli_small$day_hour, fli_small$origin))$stat
null_distn <- fli_small %>%
  specify(day_hour ~ origin, success = "morning") %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "Chisq")
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = Chisq_hat, color = "red")
null_distn %>%
  summarize(p_value = mean(stat > Chisq_hat)) 
```

@@

```{r}
d_hat <- fli_small %>% 
  group_by(season) %>% 
  summarize(mean_stat = mean(dep_delay)) %>% 
  summarize(diff(mean_stat)) %>% 
  pull()
null_distn <- fli_small %>%
  specify(dep_delay ~ season) %>% # alt: response = dep_delay, 
  # explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("summer", "winter"))
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = d_hat, color = "red")
null_distn %>%
  summarize(p_value = mean(stat > d_hat) * 2)   
```

@@

```{r}
d_hat <- fli_small %>% 
  group_by(season) %>% 
  summarize(median_stat = median(dep_delay)) %>% 
  summarize(diff(median_stat)) %>% 
  pull()
null_distn <- fli_small %>%
  specify(dep_delay ~ season) %>% # alt: response = dep_delay, 
  # explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians", order = c("summer", "winter"))
ggplot(null_distn, aes(x = stat)) +
  geom_bar() +
  geom_vline(xintercept = d_hat, color = "red")
null_distn %>%
  summarize(p_value = mean(stat > d_hat) * 2)    
```

@@

```{r}
F_hat <- anova(
               aov(formula = arr_delay ~ origin, data = fli_small)
               )$`F value`[1]
null_distn <- fli_small %>%
   specify(arr_delay ~ origin) %>% # alt: response = arr_delay, 
   # explanatory = origin
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "F")
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = F_hat, color = "red")  
null_distn %>% 
  summarize(p_value = mean(stat > F_hat))
```

@@

```{r}
slope_hat <- lm(arr_delay ~ dep_delay, data = fli_small) %>% 
  broom::tidy() %>% 
  filter(term == "dep_delay") %>% 
  select(estimate) %>% 
  pull()
null_distn <- fli_small %>%
   specify(arr_delay ~ dep_delay) %>% 
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "slope")
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = slope_hat, color = "red")  
null_distn %>% 
  summarize(p_value = mean(stat > slope_hat) * 2)   
```

@@

```{r}
d_hat <- fli_small %>% 
  group_by(season) %>% 
  summarize(mean_stat = mean(arr_delay)) %>% 
  summarize(diff(mean_stat)) %>% 
  pull()
boot <- fli_small %>%
   specify(arr_delay ~ season) %>%
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "diff in means", order = c("summer", "winter")) %>% 
   pull()
c(lower = d_hat - 2 * sd(boot), 
  upper = d_hat + 2 * sd(boot))
```

@@

```{r}
d_hat <- fli_small %>%
  group_by(season) %>%
  summarize(prop = mean(day_hour == "morning")) %>%
  summarize(diff(prop)) %>%
  pull()
boot <- fli_small %>%
  specify(day_hour ~ season, success = "morning") %>%
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "diff in props", order = c("summer", "winter")) %>%
  pull()
c(lower = d_hat - 2 * sd(boot), 
  upper = d_hat + 2 * sd(boot))
```

>>>>

---
title: "Randomization Examples using `nycflights13` `flights` data"
author: "Chester Ismay and Andrew Bray"
date: "2018-01-05"
output: 
  rmarkdown::html_vignette:
    df_print: kable
vignette: |
  %\VignetteIndexEntry{flights example}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

**Note**: The `type` argument in `generate()` is automatically filled based on the entries for `specify()` and
`hypothesize()`. It can be removed throughout the examples that follow. It is left in to reiterate the type of generation process being performed.

@@

```{r message=FALSE, warning=FALSE}
library(nycflights13)
library(dplyr)
library(ggplot2)
library(stringr)
library(infer)
set.seed(2017)
fli_small <- flights %>% 
  na.omit() %>%
  sample_n(size = 500) %>% 
  mutate(season = case_when(
    month %in% c(10:12, 1:3) ~ "winter",
    month %in% c(4:9) ~ "summer"
  )) %>% 
  mutate(day_hour = case_when(
    between(hour, 1, 12) ~ "morning",
    between(hour, 13, 24) ~ "not morning"
  )) %>% 
  select(arr_delay, dep_delay, season, 
         day_hour, origin, carrier)
```

@@

```{r}
x_bar <- fli_small %>%
  summarize(mean(dep_delay)) %>%
  pull()
```

```{r}
null_distn <- fli_small %>%
  specify(response = dep_delay) %>%
  hypothesize(null = "point", mu = 10) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "mean")
ggplot(data = null_distn, mapping = aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = x_bar, color = "red")
null_distn %>%
  summarize(p_value = mean(stat >= x_bar) * 2)
```

@@

```{r}
x_tilde <- fli_small %>%
  summarize(median(dep_delay)) %>%
  pull()
null_distn <- fli_small %>%
  specify(response = dep_delay) %>%
  hypothesize(null = "point", med = -1) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "median")
ggplot(null_distn, aes(x = stat)) +
  geom_bar() +
  geom_vline(xintercept = x_tilde, color = "red")
null_distn %>%
  summarize(p_value = mean(stat <= x_tilde) * 2)
```

@@

```{r}
p_hat <- fli_small %>%
  summarize(mean(day_hour == "morning")) %>%
  pull()
null_distn <- fli_small %>%
  specify(response = day_hour, success = "morning") %>%
  hypothesize(null = "point", p = .5) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "prop")
ggplot(null_distn, aes(x = stat)) +
  geom_bar() +
  geom_vline(xintercept = p_hat, color = "red")
null_distn %>%
  summarize(p_value = mean(stat <= p_hat) * 2)
```

@@

```{r}
d_hat <- fli_small %>%
  group_by(season) %>%
  summarize(prop = mean(day_hour == "morning")) %>%
  summarize(diff(prop)) %>%
  pull()
null_distn <- fli_small %>%
  specify(day_hour ~ season, success = "morning") %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "diff in props", order = c("winter", "summer"))
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = d_hat, color = "red")
null_distn %>%
  summarize(p_value = mean(stat <= d_hat) * 2) %>%
  pull()
```

@@

```{r}
Chisq_hat <- fli_small %>%
  chisq_stat(formula = origin ~ NULL)
null_distn <- fli_small %>%
  specify(response = origin) %>%
  hypothesize(null = "point", 
              p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "Chisq")
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = pull(Chisq_hat), color = "red")
null_distn %>%
  summarize(p_value = mean(stat >= pull(Chisq_hat))) %>%
  pull()
```

@@

```{r}
Chisq_hat <- fli_small %>%
  chisq_stat(formula = day_hour ~ origin)
null_distn <- fli_small %>%
  specify(day_hour ~ origin, success = "morning") %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "Chisq")
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = pull(Chisq_hat), color = "red")
null_distn %>%
  summarize(p_value = mean(stat >= pull(Chisq_hat))) %>%
  pull()
```

@@

```{r}
d_hat <- fli_small %>% 
  group_by(season) %>% 
  summarize(mean_stat = mean(dep_delay)) %>% 
  # Since summer - winter
  summarize(-diff(mean_stat)) %>% 
  pull()
null_distn <- fli_small %>%
  specify(dep_delay ~ season) %>% # alt: response = dep_delay, 
  # explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("summer", "winter"))
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = d_hat, color = "red")
null_distn %>%
  summarize(p_value = mean(stat <= d_hat) * 2) %>%
  pull()
```

@@

```{r}
d_hat <- fli_small %>% 
  group_by(season) %>% 
  summarize(median_stat = median(dep_delay)) %>% 
  # Since summer - winter
  summarize(-diff(median_stat)) %>% 
  pull()
null_distn <- fli_small %>%
  specify(dep_delay ~ season) %>% # alt: response = dep_delay, 
  # explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians", order = c("summer", "winter"))
ggplot(null_distn, aes(x = stat)) +
  geom_bar() +
  geom_vline(xintercept = d_hat, color = "red")
null_distn %>%
  summarize(p_value = mean(stat >= d_hat) * 2) %>%
  pull()
```

@@

```{r}
F_hat <- anova(
               aov(formula = arr_delay ~ origin, data = fli_small)
               )$`F value`[1]
null_distn <- fli_small %>%
   specify(arr_delay ~ origin) %>% # alt: response = arr_delay, 
   # explanatory = origin
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "F")
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = F_hat, color = "red")  
null_distn %>% 
  summarize(p_value = mean(stat >= F_hat)) %>%
  pull()
```

@@

```{r}
slope_hat <- lm(arr_delay ~ dep_delay, data = fli_small) %>% 
  broom::tidy() %>% 
  filter(term == "dep_delay") %>% 
  select(estimate) %>% 
  pull()
null_distn <- fli_small %>%
   specify(arr_delay ~ dep_delay) %>% 
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "slope")
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = slope_hat, color = "red")  
null_distn %>% 
  summarize(p_value = mean(stat >= slope_hat) * 2) %>%
  pull()
```

@@

```{r}
d_hat <- fli_small %>% 
  group_by(season) %>% 
  summarize(mean_stat = mean(arr_delay)) %>% 
  # Since summer - winter
  summarize(-diff(mean_stat)) %>% 
  pull()
boot <- fli_small %>%
   specify(arr_delay ~ season) %>%
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "diff in means", order = c("summer", "winter")) %>% 
   pull()
c(lower = d_hat - 2 * sd(boot), 
  upper = d_hat + 2 * sd(boot))
```

@@

```{r}
d_hat <- fli_small %>%
  group_by(season) %>%
  summarize(prop = mean(day_hour == "morning")) %>%
  # Since summer - winter
  summarize(-diff(prop)) %>%
  pull()
boot <- fli_small %>%
  specify(day_hour ~ season, success = "morning") %>%
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "diff in props", order = c("summer", "winter")) %>%
  pull()
c(lower = d_hat - 2 * sd(boot), 
  upper = d_hat + 2 * sd(boot))
```

### 2018-05-13 inst/doc/mtcars_examples.Rmd
Update vignettes

---
title: "Examples using `mtcars` data"
author: "Chester Ismay and Andrew bray"
date: "2018-01-05"
output: 
  rmarkdown::html_vignette
vignette: |
  %\VignetteIndexEntry{mtcars example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

```{r message=FALSE, warning=FALSE}
library(infer)
library(dplyr)
mtcars <- as.data.frame(mtcars) %>%
  mutate(cyl = factor(cyl),
         vs = factor(vs),
         am = factor(am),
         gear = factor(gear),
         carb = factor(carb))
# For reproducibility         
set.seed(2018)         
```

@@

```{r}
mtcars %>%
  specify(response = mpg) %>% # formula alt: mpg ~ NULL
  hypothesize(null = "point", sigma = 5) %>% 
  generate(reps = 100, type = "bootstrap") %>% 
  calculate(stat = "sd")
```

@@

>>>>

---
title: "Examples using `mtcars` data"
author: "Chester Ismay and Andrew Bray"
date: "2018-01-05"
output: 
  rmarkdown::html_vignette
vignette: |
  %\VignetteIndexEntry{mtcars example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

```{r message=FALSE, warning=FALSE}
library(infer)
library(dplyr)
mtcars <- mtcars %>%
  mutate(cyl = factor(cyl),
         vs = factor(vs),
         am = factor(am),
         gear = factor(gear),
         carb = factor(carb))
# For reproducibility         
set.seed(2018)         
```

@@

@@

**Not currently implemented**

```{r eval=FALSE}
mtcars %>%
  specify(response = mpg) %>% # formula alt: mpg ~ NULL
  hypothesize(null = "point", sigma = 5) %>% 
  generate(reps = 100, type = "bootstrap") %>% 
  calculate(stat = "sd")
```

### 2018-05-13 inst/doc/profiles_examples.Rmd
Update vignettes

```{r message=FALSE, warning=FALSE}
library(okcupiddata)
library(stringr)
library(infer)
set.seed(2017)
prof_small <- profiles %>% 
  na.omit() %>% 
  dplyr::sample_n(size = 500) %>% 
  dplyr::mutate(city = dplyr::case_when(
    str_detect(location, "san fran") ~ "san fran",
    !str_detect(location, "san fran") ~ "not san fran"
  )) %>% 
  dplyr::select(age, sex, city, drugs, height, status)
```

@@

```{r}
prof_small %>%
  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
  hypothesize(null = "point", mu = 50) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "mean") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(response = age) %>% # alt: age ~ NULL
  hypothesize(null = "point", med = 55) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "median") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(response = sex, success = "m") %>%
  hypothesize(null = "point", p = c("m" = .65)) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "prop") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(sex ~ city, success = "m") %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in props", order = c("san fran", "not san fran")) %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(drugs ~ NULL) %>% # alt: response = drugs
  hypothesize(null = "point", 
              p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "Chisq") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(drugs ~ status) %>% # alt: response = drugs, explanatory = status
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "Chisq") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("m", "f")) %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians", order = c("m", "f")) %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(age ~ status) %>% # alt: response = age, explanatory = status
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "F") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(age ~ height) %>% # alt: response = age, explanatory = height
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "slope") %>% 
  visualize()
```

@@

@@

```{r}
prof_small %>%
  specify(response = age) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "mean") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(response = age) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "median") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(response = sex, success = "f") %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "prop") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(age ~ sex) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("m", "f")) %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(sex ~ city, success = "m") %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in props", order = c("san fran", "not san fran")) %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(age ~ height) %>% 
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "slope") %>% 
  visualize()
```

>>>>

```{r message=FALSE, warning=FALSE}
library(okcupiddata)
#remotes::install_github("andrewpbray/infer", ref = "develop")
library(infer)

set.seed(2017)
prof_small <- profiles %>% 
  na.omit() %>% 
  dplyr::sample_n(size = 500) %>% 
  dplyr::mutate(city = dplyr::case_when(
    stringr::str_detect(location, "san fran") ~ "san fran",
    !stringr::str_detect(location, "san fran") ~ "not san fran"
  )) %>% 
  dplyr::select(age, sex, city, drugs, height, status)
```

@@

```{r}
x_bar <- prof_small %>% 
  dplyr::summarize(mean(age)) %>% 
  dplyr::pull()
prof_small %>%
  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
  hypothesize(null = "point", mu = 34) %>% 
  generate(reps = 1000) %>% 
  calculate(stat = "mean") %>% 
  visualize(obs_stat = x_bar, direction = "both")
```

@@

```{r}
x_tilde <- prof_small %>% 
  dplyr::summarize(median(age)) %>% 
  dplyr::pull()
prof_small %>%
  specify(response = age) %>% # alt: age ~ NULL
  hypothesize(null = "point", med = 29) %>% 
  generate(reps = 1000) %>% 
  calculate(stat = "median") %>% 
  visualize(obs_stat = x_tilde, direction = "both")
```

@@

```{r}
p_hat <- prof_small %>% 
  dplyr::summarize(mean(sex == "f")) %>% 
  dplyr::pull()
prof_small %>%
  specify(response = sex, success = "f") %>%
  hypothesize(null = "point", p = c("f" = .35)) %>% 
  generate(reps = 1000) %>% 
  calculate(stat = "prop") %>% 
  visualize(obs_stat = p_hat, direction = "right")
```

@@

```{r}
obs_diff <- prof_small %>% 
  dplyr::group_by(city) %>% 
  dplyr::summarize(prop = mean(sex == "m")) %>%
  dplyr::summarize(diff(prop)) %>%
  dplyr::pull()
prof_small %>%
  specify(sex ~ city, success = "m") %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000) %>%
  calculate(stat = "diff in props", order = c("san fran", "not san fran")) %>% 
  visualize(obs_stat = obs_diff, direction = "both")
```

@@

```{r}
Chisq_hat <- chisq.test(table(prof_small$drugs))$stat
prof_small %>%
  specify(drugs ~ NULL) %>% # alt: response = drugs
  hypothesize(null = "point", 
              p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
  generate(reps = 1000) %>%
  calculate(stat = "Chisq") %>% 
  # Only "right" or "greater" as options here
  visualize(obs_stat = Chisq_hat, direction = "right")
```

@@

```{r}
Chisq_hat <- prof_small %>% chisq_stat(formula = drugs ~ status)
prof_small %>%
  specify(drugs ~ status) %>% # alt: response = drugs, explanatory = status
  hypothesize(null = "independence") %>%
  generate(reps = 1000) %>%
  calculate(stat = "Chisq") %>% 
  # Only "right" or "greater" as options here
  visualize(obs_stat = Chisq_hat, direction = "right")
```

@@

```{r}
obs_diff <- prof_small %>% 
  dplyr::group_by(sex) %>% 
  dplyr::summarize(mean_age = mean(age)) %>% 
  dplyr::summarize(diff(mean_age)) %>% 
  dplyr::pull()
prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  generate(reps = 1000) %>%
  calculate(stat = "diff in means", order = c("m", "f")) %>% 
  visualize(obs_stat = obs_diff, direction = "both")
```

@@

```{r}
obs_diff <- prof_small %>% 
  dplyr::group_by(sex) %>% 
  dplyr::summarize(median_age = median(age)) %>% 
  dplyr::summarize(diff(median_age)) %>% 
  dplyr::pull()
prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  generate(reps = 1000) %>%
  calculate(stat = "diff in medians", order = c("m", "f")) %>% 
  visualize(obs_stat = obs_diff, direction = "two_sided")
```

@@

```{r}
F_hat <- anova(
               aov(formula = age ~ status, data = prof_small)
               )$`F value`[1]
prof_small %>%
  specify(age ~ status) %>% # alt: response = age, explanatory = status
  hypothesize(null = "independence") %>%
  generate(reps = 1000) %>%
  calculate(stat = "F") %>% 
  # Only "right" or "greater" as options here
  visualize(obs_stat = F_hat, direction = "greater")
```

@@

```{r}
slope_hat <- lm(age ~ height, data = prof_small) %>% 
  broom::tidy() %>% 
  dplyr::filter(term == "height") %>% 
  dplyr::select(estimate) %>% 
  dplyr::pull()
prof_small %>%
  specify(age ~ height) %>% # alt: response = age, explanatory = height
  hypothesize(null = "independence") %>%
  generate(reps = 1000) %>%
  calculate(stat = "slope") %>% 
  visualize(obs_stat = slope_hat, direction = "both")
```

@@

### Confidence interval shading is not implemented yet

@@

```{r}
prof_small %>%
  specify(response = age) %>%
  generate(reps = 1000) %>%
  calculate(stat = "mean") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(response = age) %>%
  generate(reps = 1000) %>%
  calculate(stat = "median") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(response = sex, success = "f") %>%
  generate(reps = 1000) %>%
  calculate(stat = "prop") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(age ~ sex) %>%
  generate(reps = 1000) %>%
  calculate(stat = "diff in means", order = c("m", "f")) %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(sex ~ city, success = "m") %>%
  generate(reps = 1000) %>%
  calculate(stat = "diff in props", order = c("san fran", "not san fran")) %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(age ~ height) %>% 
  generate(reps = 1000) %>%
  calculate(stat = "slope") %>% 
  visualize()
```

### 2018-05-13 inst/doc/two_sample_t.Rmd
Update vignettes

```{r}
obs_t <- fli_small %>% 
  t_test(formula = arr_delay ~ half_year) %>% 
  dplyr::select(statistic) %>% 
  dplyr::pull()
```

@@

```{r}
obs_t <- fli_small %>% 
  t_stat(formula = arr_delay ~ half_year)
```

@@

```{r}
t_null_distn %>% 
  dplyr::summarize(p_value = mean(abs(stat) >= obs_t)) %>% 
  dplyr::pull()
```

@@

```{r}
fli_small %>% 
  t_test(formula = arr_delay ~ half_year) %>% 
  dplyr::select(p_value) %>% 
  dplyr::pull()
```

>>>>

```{r}
obs_t <- fli_small %>% 
  t_test(formula = arr_delay ~ half_year, alternative = "two_sided",
         order = c("h1", "h2")) %>% 
  dplyr::select(statistic) %>% 
  dplyr::pull()
```

@@

```{r}
obs_t <- fli_small %>% 
  t_stat(formula = arr_delay ~ half_year, order = c("h1", "h2"))
```

@@

```{r}
t_null_distn %>% 
  dplyr::summarize(p_value = mean(abs(stat) >= pull(obs_t))) %>% 
  dplyr::pull()
```

@@

```{r}
fli_small %>% 
  t_test(formula = arr_delay ~ half_year,
         alternative = "two_sided",
         order = c("h1", "h2")) %>% 
  dplyr::select(p_value) %>% 
  dplyr::pull()
```
